Efficient stability for the Pauli group

### 2023-06-04 efficient_stability.tex
started proof of Theorem 5.1

\newcommand{\F}{\ensuremath{\mathbb{F}}}
\newcommand{\M}{\ensuremath{\mathbb{M}}}
\newcommand{\ot}{\otimes}
\newcommand{\Fp}{\F_p}
\newcommand{\Fq}{\field}
\newcommand{\BH}{\textsc{BH}}
\newcommand{\ld}{\textsc{ld}}
\newcommand{\downsize}{\kappa}
\newcommand{\tobin}{\flat}
\newcommand{\downsizem}{\chi}

@@

\newcommand{\Inv}{\ensuremath{\textsc{Inv}}}
\newcommand{\GEN}{\ensuremath{\textsc{GEN}}}
\newcommand{\SAMP}{\ensuremath{\textsc{SAMP}}}
\newcommand{\epr}{\ensuremath{\textsc{epr}}}
\newcommand{\RM}{\ensuremath{\textsc{RM}}}
\newcommand{\Had}{\ensuremath{\textsc{Had}}}
\newcommand{\HRM}{\ensuremath{\textsc{HRM}}}

@@

\DeclareMathOperator{\arcsinh}{arcsinh}
\DeclareMathOperator{\tr}{tr}

@@

\author{Thomas Vidick and Henry Yuen}
\date{\today}
\maketitle

@@

@@

\section{Efficient stability}

@@

For convenience we adopt the following notation from~\cite{slofstra2019set}. A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$. Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$. We use the notation 
\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finite group to a unital tracial $C^*$-algebra $\mA$ is introduced. Informally, an $\eps$-almost homomorphism of a finitely presented group $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$. We give a variant of their definition that quantifies the error in an average sense.

@@

A stability result states that $\eps$-homomorphisms are close to exact hommorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.

@@

We do not know many general results about stability. We give two. First of all, 
for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$. We refer to this presentation as the \emph{exhaustive presentation}. If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}. In particular, for finite groups the following result is known~\cite{gh,thom}.

\begin{theorem}\label{thm:gh}[Theorem~1.4 in~\cite{de2022spectral}]
Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras. Let $U_S$ and $U_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively. Then $G=\langle S:R\rangle$ is $(O(\eps),U_R,U_C,\mC)$-stable. 
\end{theorem}

Next we state a result from de la Salle~\cite{de2022spectral} which allows to combine stability results. The results in~\cite{de2022spectral} are general, and in particular allow to show that the direct product of stable groups is stable. Here, we will only use the following specialization to the case of $\Z_2^k$, which is the only setting that we will use. For a measure $\mu$ on $\Z_2^k$, define its spectral gap 
\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]

\begin{theorem}[\cite{de2022spectral} Corollary 2.6]
Let $\mu$ be a measure on $\Z_2^k$ with spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
\[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
Then there are representations $U_X,U_Z:\Z_2^k\to\mN$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are close, $\phi_Z$ and $U_Z$ are close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
\end{theorem}

\subsection{Simple examples}

As a first simple application we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$ and $\mC$ the class of finite-dimensional matrix algebras. To emphasize the analogy between the following result and the \emph{Blum-Luby-Rubinfeld linearity test} in property testing~\cite{} we state the result for a restricted class of approximate homomorphisms, and give the consequence in a way that leverages the simple representation theory of $\Z_2^k$.

\begin{corollary}\label{cor:lin-test}
Let $d\geq 1$ and $\phi:\Z_2^k \to \Obs(\C^d)$ be such that 
\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau_d}^2 \,\leq\,\eps\;.\]
Then there is a $d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\C^{d'}$ such that 
\[ \Es{x\in \Z_2^k} \Big\| \phi(x) - w^* \Big(\sum_u (-1)^{u\cdot x} P_u\Big) w \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
\end{corollary}

\begin{proof}
Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(M_d(\C),\tau_d)$ for the exhaustive presentation. Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism into $M_{d'}(\C)$. Such a homomorphism is given by commuting Hermitian unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$. Then it is easy to verify that for $u\in \Z_2^k$, $P_u = \Es{x} (-1)^{u\cdot x} U_x$ is a projection such that $\sum_u P_u=\Id$ and the $\{P_u\}$ satisfy the conclusion of the corollary. 
\end{proof}

@@

We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic. As one would naturally expect, this presentation has a weaker modulus of stability.

\begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
\end{lemma}

The dependence of $\delta_k$ on $k$ that comes out of the proof from~\cite{slofstra2019set} is exponential, i.e. $\delta_k(\eps)\leq C^k \eps$ for some $C>1$. In Section~\ref{} we give a presentation that has an intermediate trade-off.

We end with a non-Abelian group that is central to applications in quantum information, the \emph{Pauli group}. For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows. Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$. Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$. Alternatively, $\pauli_k$ is the group generated by the Pauli matrices 
\[ \sigma_X(a) = , \sigma_Z(b) =\]
for $a,b\in \Z_2^k$. It is also known as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \}\subseteq GL_{k+2}(\F_2)$. Concretely, we label elements of the Pauli group as triples $(J,a,b)$ where $J$ is a special label and $a,b\in\Z_2^k$, and consider the following presentation for it:
\[ \pauli_k \,=\, \langle (a,b), a,b\in \Z_2^k : (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \rangle_{\Z_2}\;.\] 
This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, when $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras.

@@

\begin{lemma}[\cite{Chao-Reichardt}]\label{lem:eff-pauli}
For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
\end{lemma}

\section{Efficient stability for the Pauli group}

The goal of this section is to re-formulate, in the language of this paper, a result that plays an important role in~\cite{mipre}. To state the result we first introduce a specific linear error-correcting code.

@@

Every linear $[n,k,d]_2$ code implies a presentation of $\Z_2^k$. This is already explained in~\cite{dlS}.

For readability it is convenient to reformulate the parity check matrix as a \emph{tester} for the code. This allows us to give a more succinct, ``algorithmic'' definition of a parity check matrix for a given code. Specifically we give the following definition.

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
An \emph{$r$-local linear tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\F_q$ is a linear function such that $u\in \code$ if and only if for all $S$ in the support of $\mu$, $M_S(u_S)=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester. However, we will not need to be more specific than this.}
\end{definition}

\subsection{The Reed-Muller code over $\F_q$}

Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$. It follows that the map $\mC_\RM: (c_\alpha) \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma:

@@

\begin{proposition}\label{prop:q-to-2}
Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$. Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps))$. 
\end{proposition}

>>>>

\newcommand{\F}{\ensuremath{\mathbb{F}}}
\newcommand{\M}{\ensuremath{\mathbb{M}}}
\newcommand{\ot}{\otimes}
\newcommand{\Fp}{\F_p}
\newcommand{\Fq}{\field}
\newcommand{\BH}{\textsc{BH}}
\newcommand{\ld}{\textsc{ld}}
\newcommand{\com}{\textsc{com}}
\newcommand{\sq}{\textsc{sq}}
\newcommand{\downsize}{\kappa}
\newcommand{\tobin}{\flat}
\newcommand{\downsizem}{\chi}

@@

\newcommand{\Inv}{\ensuremath{\textsc{Inv}}}
\newcommand{\GEN}{\ensuremath{\textsc{GEN}}}
\newcommand{\SAMP}{\ensuremath{\textsc{SAMP}}}
\newcommand{\epr}{\ensuremath{\textsc{epr}}}
\newcommand{\RM}{\ensuremath{\textsc{RM}}}
\newcommand{\bRM}{\ensuremath{\textsc{RM2}}}
\newcommand{\Had}{\ensuremath{\textsc{Had}}}
\newcommand{\HRM}{\ensuremath{\textsc{HRM}}}

@@

\DeclareMathOperator{\arcsinh}{arcsinh}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\sgn}{sgn}

@@

\author[1]{Michael Chapman}
\author[2]{Thomas Vidick}
\author[3]{Henry Yuen}
\affil[1]{}
\affil[2]{}
\affil[3]{}

\date{\today}
\maketitle

@@

	We will make use of the following. It is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement. See e.g.~\cite{kempe2011parallel,ji2020quantum} or~\cite[Theorem 1.2]{de2021orthogonalization} for the version that we use here.

\begin{lemma}\label{lem:pull-back}
Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry. Let 
\[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
 Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
\begin{equation}
\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_2^2 \,\leq \ 56\eps\;.
\end{equation}
\end{lemma}

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* P_a  ( P - w w^*) P_a w \big)\\
\intertext{
\hnote{I don't get this next line... how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$. So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing. It's this sentence about the ``corner'' in the prelims...should we add something more explicit? Or explain this line here more, since it's the first time we make the manipulation? }\hnote{I think it would be good to add at least one line of explanation...}\tnote{added (extra line above and justification below)}
}
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the third line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
\begin{equation*}
\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
\end{equation*}
Finally,
\begin{align*}
\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
&\leq 56 \eps\;,
\end{align*}
where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
\end{proof}

@@

\section{Stability}

@@

\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}. A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$. Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$. We use the notation 
\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]

In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ is introduced. Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$. We give a variant of their definition that quantifies the error in an average sense.

@@

A stability result states that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.

@@

We do not know many general results about stability. We give two. First of all, 
for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$. We refer to this presentation as the \emph{exhaustive presentation}. If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}. In particular, for finite groups the following result is known~\cite{gowers2017inverse,de2019operator}. We adopt the formulation from~\cite[Theorem 1.4]{de2022spectral}.

\begin{theorem}\label{thm:gh}
Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras. Let $U_S$ and $U_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively. Then $G=\langle S:R\rangle$ is $(O(\eps),U_R,U_C,\mC)$-stable. 
\end{theorem}

Next we state a result from de la Salle~\cite{de2022spectral} which allows to combine stability results. The results in~\cite{de2022spectral} are general, and in particular allow to show that the direct product of stable groups is stable. Here, we will only use the following specialization to the case of $\Z_2^k$. For a measure $\mu$ on $\Z_2^k$, define its spectral gap 
\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]

\begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
Let $\mu$ be a measure on $\Z_2^k$ with spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
\[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $\delta$-close, $\phi_Z$ and $U_Z$ are $\delta$close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
\end{theorem}

\subsection{Examples}

As a first example we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$.

\begin{corollary}\label{cor:lin-test} \tnote{Stated this for finite dimensions. Not sure what we want in the end}
Let $d\geq 1$ and $\phi:\Z_2^k \to \mU(\C^d)$ be such that 
\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
Then there is a %$d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a 
projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\mA$ such that 
\[ \Es{x\in \Z_2^k} \Big\| \phi(x) -\Big(\sum_u (-1)^{u\cdot x} P_u\Big)  \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
\end{corollary}

\begin{proof}
Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mA,\tau_d)$ for the exhaustive presentation. Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to $(\mN,\tau^\mN)$. Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$. Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.

For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$. Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$. Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mA$ that satisfies the conclusions of the corollary. \tnote{more details needed} 
\end{proof}

@@

We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic. This presentation is also stable.

\begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable. Furthermore, the close representation can be taken on the same algebra. 
\end{lemma}

As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the girth of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}. By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}. With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}. This is nearly tight, as shown in~\cite{chao2017overlapping}.

We end with a non-Abelian group that plays an important role in applications in quantum information, the \emph{Pauli group}. For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows. Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$. Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$. Alternatively, $\pauli_k$ is the group generated by the Pauli matrices 
\[ \sigma_X(a) = , \sigma_Z(b) =\]
for $a,b\in \Z_2^k$. It is also known as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \}\subseteq GL_{k+2}(\F_2)$. Concretely, we label elements of the Pauli group as triples $(J,a,b)$ where $J$ is a special label and $a,b\in\Z_2^k$, and consider the following presentation for it:
\[ \pauli_k \,=\, \langle (a,b), a,b\in \Z_2^k : (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \rangle_{\Z_2}\;.\] 
This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, when $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.

@@

\begin{lemma}\label{lem:eff-pauli}
For every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
\end{lemma}

\begin{proof}
This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}.
\end{proof}

\section{Presentations from codes}

The goal of this section is to reformulate, in the language of this paper, a result that plays an important role in~\cite{ji2020mip}. To state the result we first introduce a specific linear error-correcting code.

@@

For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code is a $k$-dimensional subspace $\code$ of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|\geq d$. A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ by setting $\code = \ker h$.

We now specialize to the case where $q=2$. 
A parity check matrix for a code of dimension $k$ implies a presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq k} x_j^{h_{ij}}=e \]
that ``verifies'' the parity check associated with the $i$-th row of $j$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_j'$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$ as 
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$. If however we further impose pairwise commutation relations then it is not hard to see the following.

\begin{lemma}\label{lem:com-code}
Let $R''_{jj'}$ be the commutation relation $[x_j,x_{j'}]=e$. Then
\[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.\]
\end{lemma}

\begin{proof}
The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$. In fact, it is equal to the quotient of $Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$. So it is $\Z_2^k$ where $k$ is the dimension of the kernel of $h$.  
\end{proof}

\begin{remark}
There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.  
\end{remark}

For readability it is convenient to reformulate the parity check matrix as a \emph{tester} for the code. This allows us to give a more succinct, ``algorithmic'' definition of a parity check matrix for a given code. Informally, the tester takes as input a word $w\in \F_2^n$ and determines if $w\in \mC$ by selecting a parity check at random and evaluating it. 
 Specifically we give the following definition. (For the sake of later use, we state the definition for the case of a general prime power $q$.)

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester. However, we will not need to be more specific than this.}
\end{definition}

We conclude with an example, the \emph{Hadamard code}. This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$. For simplicity we write  $\code_\had$ to denote this code, omitting $t$. As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.

A parity check matrix for $\code_\had$ is the matrix $h_\had\in \F_2^{T^2\times T}$ defined as follows. Identify the rows of $h_\had$ with pairs $(x,y)\in \F_2^t\times \F_2^t$, and the columns of $h_\had$ with $\F_2^t$. Then the $(x,y)$-th row of $h$ has nonzero entries at positions $x,y$ and $x+y$ only. The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$. This tester can be described more algorithmically as in Figure~\ref{fig:test-had}.

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
	Given access to some $g\in \F_2^n$, where $n=2^t$, identify $g$ with a function $g:\F_2^t\to\F_2$. Perform the following. 
\begin{enumerate}
\item Select $(x,y)\in \F_2^t \times \F_2^t$ uniformly at random. 
\item Accept if and only if $g(x)+g(y)+g(x+y)=0$.  	
    \end{enumerate}
  \end{gamespec}
  \caption{A $3$-local linear tester for $\code_{\had}$}
  \label{fig:test-had}
\end{figure}

\begin{remark}
Because each pair of coordinates $(x,y)$ appears together in at least one parity check, we can apply Lemma~\ref{lem:com-code} to deduce that $G(h_\had)=\Z_2^t$. 
\end{remark}

We state our first stability result for a code-based presentation, the presentation $G(h_\had)$ defined as~\eqref{eq:def-gh-pres} where $h_\had$ is defined above. To state the result we need to specify distributions $\mu_S$ and $\mu_R$. We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ uniform over the relations $R_i$, for $i\in \{1,\ldots,T^2\}$. Note that here, we do not need to place any weight on the commutation relations.

\begin{lemma}\label{lem:had-stab}
Let $\mC$ be the class of all tracial von Neumann algebras. 
The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
\end{lemma}

\begin{proof}
The result is an immediate application of Theorem~\ref{thm:gh}.

\subsection{The Reed-Muller code over $\F_q$}
\label{sec:rmq}

Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$. It follows that the map $\mC_\RM: (c_\alpha) \mapsto (f(x))_{x\in \F_q^m}$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.

@@
